\documentclass[a4paper]{exam}

\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titling}

\printanswers

\title{Weekly Challenge 02: Logical Thinking\\CS/MATH 113 Discrete Mathematics}
\author{$\langle Q1 Team 17 \rangle$}  % <== for grading, replace with your team name, e.g. q1-team-420
\date{Habib University | Spring 2023}

\qformat{{\large\bf \thequestion. \thequestiontitle}\hfill}
\boxedpoints

\begin{document}
\maketitle

\begin{questions}
  
  \titledquestion{Logical Hikers}
  A group of $n$ hikers is standing at the base of a mountain. Their guide joins them and hangs a compass from each hiker's neck. At their current position, all the compasses should point North. But some are faulty. A hiker cannot see their own compass but can see everyone else's. For the hike to go smoothly, it is important for every hiker to know the condition of their compass, i.e., if it is faulty or functions correctly. The guide is going around asking each hiker in turn about the condition of their compass. Each hiker reports either ``Working'', ``Faulty'', or ``Can't tell''. The hikers are highly logical and always respond truthfully.

  \begin{parts}
    \part Given that the guide has announced that \textit{exactly} $k$ compasses are faulty where $0\leq k \leq n$, prove that every hiker can correctly tell the condition of their compass just by looking at the compasses of the other hikers.
    \part Suppose instead that the guide announces \textit{at least} $k$ faulty compasses where $1\leq k \leq (n-1)$. Prove the following statement about the responses: As soon as a hiker responds, ``Faulty'', no subsequent hiker will respond, ``Can't tell''.
    \part Suppose instead that the guide announces \textit{at most} $k$ faulty compasses where $1\leq k \leq (n-1)$. Provide a statement about the responses similar to the one given in the previews part. Show that it is correct.
  \end{parts}

  \begin{solution}
\newline
(a)
\newline
If a hiker's compass is faulty, they can tell by looking at the compasses of the other hikers. If the number of faulty compasses excluding his equals $k-1$, then he would be sure that he has a faulty compass. If a hiker's compass is working, they will be able to tell by looking at the compasses of the other hikers and seeing that there are $k$ faulty compasses, since they know that the number of faulty compasses is $k$. Therefore he knows that his compass will be working.
\newline
(b)
\newline 
In this case the first hiker would only say "faulty" if he sees $k-1$ faulty compasses on the other hikers, subsequently the other hikers with faulty compasses would do the same. The ones who have a working compass would know it because the hiker who has a faulty compass would let him know because they can only say that when there are $k-1$ faulty compasses in front of them which means he can't have a faulty compass as he can see $k$ people with faulty compasses in front of him.
\newline
(c)
\newline
If a hiker says "working", no subsequent hiker will say "cant tell".
This is because the hiker will only say "working" if he sees $k$ faulty compasses on the other hikers. Subsequently, if the other hikers see $k$ faulty compasses on the others they'll say "working", else if they see $k-1$ faulty compasses they would say "faulty".
  \end{solution}
\end{questions}

\end{document}
